Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-15 csf-2017/paper.tex
Rename "discussion and future work" section to just discussion and save a line somewhere.

\section{Discussion, future work}
\label{sec:discussion}

@@

More closely related to our work are papers that use a trusted stack manager and
some form of memory isolation to enforce control flow correctness as part of a
secure compilation
result~\citep{patrignani_modular_2016-1,juglaret_beyond_2016-1}. Our work
differs from theirs in that we use a different form of low-level security
primitive (a capability machine with local capabilities rather than a machine
with a primitive notion of compartments) and we do not use a trusted stack
manager component, but a decentralised calling convention based on local
capabilities. Also, they both prove a secure compilation result from a
high-level language, which clearly implies a general form of control flow
correctness, while we define a sound logical relation that can be used to reason
about specific programs that rely on well-bracketed control flow.

>>>>

\section{Discussion}
\label{sec:discussion}

@@

More closely related to our work are papers that use a trusted stack manager and
some form of memory isolation to enforce control flow correctness as part of a
secure compilation
result~\citep{patrignani_modular_2016-1,juglaret_beyond_2016-1}. Our work
differs from theirs in that we use a different form of low-level security
primitive (a capability machine with local capabilities rather than a machine
with a primitive notion of compartments) and we do not use a trusted stack
manager component, but a decentralised calling convention based on local
capabilities. Also, both prove a secure compilation result from a high-level
language, which clearly implies a general form of control flow correctness,
while we define a sound logical relation that can be used to reason about
specific programs that rely on well-bracketed control flow.
